Inferring cosmology from gravitational waves using non-parametric detector-frame mass distribution

### 2024-10-29 src/tex/ms.tex
[showyourwork] overleaf sync

We then perform the remaining steps similar to Sec.~\ref{sec:inference_multi}.
We set the bounds for $\kappa$ to $[-10, 10]$, and the bounds for other free parameters are the same as in Table~\ref{tab:bounds}.
The result of the remapping is shown in Fig.~\ref{fig:real_result_multi}, and it is consistent with the posterior distribution reported in \cite{KAGRA:2021duu}.
\begin{figure}
    \script{plot_real_result_multi.py}
    \includegraphics[width=\linewidth]{figures/real_result_multi.pdf}
    \caption{
        Optimized parameter distribution for the real data inference.
    }
    \label{fig:real_result_multi}
\end{figure}
The result implies that \output{real_H0.txt}, which has an uncertainty much smaller than the one reported in \cite{KAGRA:2021duu}.
This is because the uncertainty only includes the uncertainty from the reconstruction, which underestimates the true uncertainty which also includes the mismatch between the population model and the observed population distribution.

This analysis we report here is a proof of concept of the method presented in this paper, and we simply aim at demonstrating that our method can be applied to the real data with relatively little effort.
To perform a detailed analysis, a more comprehensive configuration that considers different population models, cosmological models, and selection functions is required, as well as a more robust optimization scheme to include more astrophysical parameters.

>>>>

We then perform the remaining steps similar to Sec.~\ref{sec:inference_multi}.
We set the bounds for $\kappa$ to $[-10, 10]$, and the bounds for other free parameters are the same as in Table~\ref{tab:bounds}.
The result of the remapping is shown in Fig.~\ref{fig:real_result_multi}, and it is consistent with the posterior distribution reported in \cite{KAGRA:2021duu}.
\begin{figure}
    \script{plot_real_result_multi.py}
    \includegraphics[width=\linewidth]{figures/real_result_multi.pdf}
    \caption{
        Optimized parameter distribution for the real data inference.
    }
    \label{fig:real_result_multi}
\end{figure}
The result implies that \variable{output/real_H0.txt}, which has an uncertainty much smaller than the one reported in \cite{KAGRA:2021duu}.
This is because the uncertainty only includes the uncertainty from the reconstruction, which underestimates the true uncertainty which also includes the mismatch between the population model and the observed population distribution.

This analysis we report here is a proof of concept of the method presented in this paper, and we simply aim to demonstrate that our method can be applied to real data with relatively little effort.
To perform a detailed analysis, a more comprehensive configuration that considers different population models, cosmological models, and selection functions is required, as well as a more robust optimization scheme to include more astrophysical parameters.
